CA Affordabulity

### 2020-09-20 paper.Rmd
update

>>>>

save(own,"Data/own.rds")

# census data
census_api_key("b25f8b1b7bf10561c9cbc3a20a4d2572677f1f05")
options(tigris_use_cache = TRUE)

vars <- load_variables(2018, "acs5", cache = TRUE)

census_vars <- c(median_income="B19013_001",
                 pop_in_hh_with_income_assistance="B09010_002",
                 pop_in_hh_with_no_income_assistance="B09010_008",
                 hh_inc_5k="B19001_002",
                 hh_inc_12.5k="B19001_003",
                 hh_inc_17.5k="B19001_004",
                 hh_inc_22.5k="B19001_005",
                 hh_inc_27.5k="B19001_006",
                 hh_inc_32.5k="B19001_007",
                 hh_inc_37.5k="B19001_008",
                 hh_inc_42.5k="B19001_009",
                 hh_inc_47.5k="B19001_010",
                 hh_inc_55k="B19001_011",
                 hh_inc_67.5k="B19001_012",
                 hh_inc_87.5k="B19001_013",
                 hh_inc_112.5k="B19001_014",
                 hh_inc_137.5k="B19001_015",
                 hh_inc_175k="B19001_016",
                 hh_inc_gr200k="B19001_017",
                 hh_income_count = "B19001_001",
                 hh_med_income_count = "B19019_001",
                 hh_size_1_med_income = "B19019_002",
                 hh_size_2_med_income = "B19019_003",
                 hh_size_3_med_income = "B19019_004",
                 hh_size_4_med_income = "B19019_005",
                 hh_size_5_med_income = "B19019_006",
                 hh_size_6_med_income = "B19019_007",
                 hh_size_7plus_med_income = "B19019_008",
                 avg_hh_size = "B25010_001",
                 hh_inc_5k_rentcalc = 'B25122_002',
                 hh_inc_15k_rentcalc = 'B25122_019',
                 hh_inc_27.5k_rentcalc = 'B25122_036',
                 hh_inc_42.5k_rentcalc = 'B25122_053',
                 hh_inc_67.5k_rentcalc = 'B25122_070',
                 hh_inc_87.5k_rentcalc = 'B25122_087',
                 hh_inc_150k_rentcalc = 'B25122_104',
                 hh_inc_5k_with_rent = 'B25122_004',
                 hh_inc_5k_gross_rent_50 = 'B25122_004',
                 hh_inc_5k_gross_rent_150 = 'B25122_005',
                 hh_inc_5k_gross_rent_250 = 'B25122_006',
                 hh_inc_5k_gross_rent_350 = 'B25122_007',
                 hh_inc_5k_gross_rent_450 = 'B25122_008',
                 hh_inc_5k_gross_rent_550 = 'B25122_009',
                 hh_inc_5k_gross_rent_650 = 'B25122_010',
                 hh_inc_5k_gross_rent_750 = 'B25122_011',
                 hh_inc_5k_gross_rent_850 = 'B25122_012',
                 hh_inc_5k_gross_rent_950 = 'B25122_013',
                 hh_inc_5k_gross_rent_1100 = 'B25122_014',
                 hh_inc_5k_gross_rent_1325 = 'B25122_015',
                 hh_inc_5k_gross_rent_1750 = 'B25122_016',
                 hh_inc_5k_gross_rent_2500 = 'B25122_017',
                 hh_inc_15k_with_rent = 'B25122_020',
                 hh_inc_15k_gross_rent_50 = 'B25122_021',
                 hh_inc_15k_gross_rent_150 = 'B25122_022',
                 hh_inc_15k_gross_rent_250 = 'B25122_023',
                 hh_inc_15k_gross_rent_350 = 'B25122_024',
                 hh_inc_15k_gross_rent_450 = 'B25122_025',
                 hh_inc_15k_gross_rent_550 = 'B25122_026',
                 hh_inc_15k_gross_rent_650 = 'B25122_027',
                 hh_inc_15k_gross_rent_750 = 'B25122_028',
                 hh_inc_15k_gross_rent_850 = 'B25122_029',
                 hh_inc_15k_gross_rent_950 = 'B25122_030',
                 hh_inc_15k_gross_rent_1100 = 'B25122_031',
                 hh_inc_15k_gross_rent_1325 = 'B25122_032',
                 hh_inc_15k_gross_rent_1750 = 'B25122_033',
                 hh_inc_15k_gross_rent_2500 = 'B25122_034',         
                 hh_inc_27.5k_with_rent = 'B25122_037',
                 hh_inc_27.5k_gross_rent_50 = 'B25122_038',
                 hh_inc_27.5k_gross_rent_150 = 'B25122_039',
                 hh_inc_27.5k_gross_rent_250 = 'B25122_040',
                 hh_inc_27.5k_gross_rent_350 = 'B25122_041',
                 hh_inc_27.5k_gross_rent_450 = 'B25122_042',
                 hh_inc_27.5k_gross_rent_550 = 'B25122_043',
                 hh_inc_27.5k_gross_rent_650 = 'B25122_044',
                 hh_inc_27.5k_gross_rent_750 = 'B25122_045',
                 hh_inc_27.5k_gross_rent_850 = 'B25122_046',
                 hh_inc_27.5k_gross_rent_950 = 'B25122_047',
                 hh_inc_27.5k_gross_rent_1100 = 'B25122_048',
                 hh_inc_27.5k_gross_rent_1325 = 'B25122_049',
                 hh_inc_27.5k_gross_rent_1750 = 'B25122_050',
                 hh_inc_27.5k_gross_rent_2500 = 'B25122_051',                  
                 hh_inc_42.5k_with_rent = 'B25122_054',
                 hh_inc_42.5k_gross_rent_50 = 'B25122_055',
                 hh_inc_42.5k_gross_rent_150 = 'B25122_056',
                 hh_inc_42.5k_gross_rent_250 = 'B25122_057',
                 hh_inc_42.5k_gross_rent_350 = 'B25122_058',
                 hh_inc_42.5k_gross_rent_450 = 'B25122_059',
                 hh_inc_42.5k_gross_rent_550 = 'B25122_060',
                 hh_inc_42.5k_gross_rent_650 = 'B25122_061',
                 hh_inc_42.5k_gross_rent_750 = 'B25122_062',
                 hh_inc_42.5k_gross_rent_850 = 'B25122_063',
                 hh_inc_42.5k_gross_rent_950 = 'B25122_064',
                 hh_inc_42.5k_gross_rent_1100 = 'B25122_065',
                 hh_inc_42.5k_gross_rent_1325 = 'B25122_066',
                 hh_inc_42.5k_gross_rent_1750 = 'B25122_067',
                 hh_inc_42.5k_gross_rent_2500 = 'B25122_068',
                 hh_inc_62.5k_with_rent = 'B25122_071',
                 hh_inc_62.5k_gross_rent_50 = 'B25122_072',
                 hh_inc_62.5k_gross_rent_150 = 'B25122_073',
                 hh_inc_62.5k_gross_rent_250 = 'B25122_074',
                 hh_inc_62.5k_gross_rent_350 = 'B25122_075',
                 hh_inc_62.5k_gross_rent_450 = 'B25122_076',
                 hh_inc_62.5k_gross_rent_550 = 'B25122_077',
                 hh_inc_62.5k_gross_rent_650 = 'B25122_078',
                 hh_inc_62.5k_gross_rent_750 = 'B25122_079',
                 hh_inc_62.5k_gross_rent_850 = 'B25122_080',
                 hh_inc_62.5k_gross_rent_950 = 'B25122_081',
                 hh_inc_62.5k_gross_rent_1100 = 'B25122_082',
                 hh_inc_62.5k_gross_rent_1325 = 'B25122_083',
                 hh_inc_62.5k_gross_rent_1750 = 'B25122_084',
                 hh_inc_62.5k_gross_rent_2500 = 'B25122_085', 
                 hh_inc_82.5k_with_rent = 'B25122_088',
                 hh_inc_82.5k_gross_rent_50 = 'B25122_089',
                 hh_inc_82.5k_gross_rent_150 = 'B25122_090',
                 hh_inc_82.5k_gross_rent_250 = 'B25122_091',
                 hh_inc_82.5k_gross_rent_350 = 'B25122_092',
                 hh_inc_82.5k_gross_rent_450 = 'B25122_093',
                 hh_inc_82.5k_gross_rent_550 = 'B25122_094',
                 hh_inc_82.5k_gross_rent_650 = 'B25122_095',
                 hh_inc_82.5k_gross_rent_750 = 'B25122_096',
                 hh_inc_82.5k_gross_rent_850 = 'B25122_097',
                 hh_inc_82.5k_gross_rent_950 = 'B25122_098',
                 hh_inc_82.5k_gross_rent_1100 = 'B25122_099',
                 hh_inc_82.5k_gross_rent_1325 = 'B25122_100',
                 hh_inc_82.5k_gross_rent_1750 = 'B25122_101',
                 hh_inc_82.5k_gross_rent_2500 = 'B25122_102', 
                 hh_inc_150k_with_rent = 'B25122_105',
                 hh_inc_150k_gross_rent_50 = 'B25122_106',
                 hh_inc_150k_gross_rent_150 = 'B25122_107',
                 hh_inc_150k_gross_rent_250 = 'B25122_108',
                 hh_inc_150k_gross_rent_350 = 'B25122_109',
                 hh_inc_150k_gross_rent_450 = 'B25122_110',
                 hh_inc_150k_gross_rent_550 = 'B25122_111',
                 hh_inc_150k_gross_rent_650 = 'B25122_112',
                 hh_inc_150k_gross_rent_750 = 'B25122_113',
                 hh_inc_150k_gross_rent_850 = 'B25122_114',
                 hh_inc_150k_gross_rent_950 = 'B25122_115',
                 hh_inc_150k_gross_rent_1100 = 'B25122_116',
                 hh_inc_150k_gross_rent_1325 = 'B25122_117',
                 hh_inc_150k_gross_rent_1750 = 'B25122_118',
                 hh_inc_150k_gross_rent_2500 = 'B25122_119' 

tracts <- get_acs(state = "CA", geography = "tract",
                  variables = census_vars, geometry = TRUE)
save(tracts,file="Data/census_tracts.rds")

# census_vars2 <- c(median_income="B19013_001",
#                  pop_in_hh_with_income_assistance="B09010_002",
#                  pop_in_hh_with_no_income_assistance="B09010_008",
#                  hh_inc_5k="B19001_002",
#                  hh_inc_12.5k="B19001_003",
#                  hh_inc_17.5k="B19001_004",
#                  hh_inc_22.5k="B19001_005",
#                  hh_inc_27.5k="B19001_006",
#                  hh_inc_32.5k="B19001_007",
#                  hh_inc_37.5k="B19001_008",
#                  hh_inc_42.5k="B19001_009",
#                  hh_inc_47.5k="B19001_010",
#                  hh_inc_55k="B19001_011",
#                  hh_inc_67.5k="B19001_012",
#                  hh_inc_87.5k="B19001_013",
#                  hh_inc_112.5k="B19001_014",
#                  hh_inc_137.5k="B19001_015",
#                  hh_inc_175k="B19001_016",
#                  hh_inc_gr200k="B19001_017",
#                  hh_income_count = "B19001_001")

bg <- get_acs(state = "CA", geography = "block group",
                  variables = census_vars, geometry = TRUE)

save(bg,file="Data/census_blockgroups.rds")

b.x <- st_buffer(st_transform(bounds,3310),dist=0)
t.x <- tracts %>%
  select(GEOID,geometry) %>%
  st_transform(3310) %>%
  st_buffer(dist=0) %>%
  mutate(AreaTract = st_area(.))

  st_buffer(st_transform(tracts,3310),dist=0)
bg.x <- st_buffer(st_transform(bg,3310),dist=0)
t.x$AreaTract_Total <- st_area(t.x)
bg.x$AreaBlockGroup_Total <- st_area(bg.x)

tracts.bounds <- st_intersection(b.x,t.x) 
tracts.bounds$Area_TractPWS <- st_area(tracts.bounds)
tracts.bounds$Percent_TractinPWS <- tracts.bounds$Area_TractPWS/tracts.bounds$AreaTract_Total

bg.bounds <- st_intersection(bg.x,t.x) 
bg.bounds$Area_BlockGroupPWS <- st_area(bg.bounds)
bg.bounds$Percent_BlockGroupinPWS <- bg.bounds$Area_BlockGroupPWS/bg.bounds$AreaBlockGroup_Total

### Find 20% and 50% Income quintile ranges by CWS (use block groups)

### Find "disposable income" at 20% range

##### 1. 
##Take rent distribution within the range corresponding to the bracket that the 20% income quintile is.

## Take median gross rent.
## Calc "disoposable income" = 20% income/12 - median gross rent + water at 6hcf bill
## Calc AR20_hh3 = 6hcf bill/disposable income
## Cacl AR20_hh6 = 12hcf bill/ disposable incoem

tracts.b<-tracts[bounds,]

tracts.b %>%
  ggplot(aes(fill = estimate)) +
  geom_sf(color = NA) +
  coord_sf(crs = 26911) +
  scale_fill_viridis_c(option = "magma")

## Assign tracts to pws
